Home Ranges
========================================================

#### Up to [data sets](../index.html)
#### Forward to [models](HRModels.html)
----
Source files available on [Github](https://github.com/camposfa/HomeRanges)

[Contact me](mailto:camposfa@gmail.com) if you are interested in the raw data

```{r echo=FALSE}
opts_chunk$set(fig.path = 'figure/', 
               fig.height = 6, 
               fig.width = 12, 
               tidy = FALSE, 
               warning = FALSE,
               cache = TRUE)
read_chunk('HomeRanges.R')
```

<br>
## Prepare workspace
```{r prepare_workspace, message = FALSE, results = 'hide'}
```

<br>
## Load data and plot tracks
```{r load_data}
```

```{r cleanup_1, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Check data and plot researcher contributions
```{r review_data}
```

<br>
## Number of points by group and observer
```{r plot_contributions2}
```

<br>
## Calculate time intervals for each home range
```{r calculate_intervals}
```

```{r cleanup_2, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Calculate number of locations for each home range
```{r calculate_num_locs}
```

<br>
## Filter out periods with few locations
```{r apply_num_locs_threshold}
```

```{r cleanup_3, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Plot of seasonal ranges to be included in the study
```{r plot_times, fig.height = 9}
```

<br>
<br>

**********************

# Calculation of predictor variables

<br>
## Calculate group size within HR intervals
```{r calculate_group_size}
```

```{r cleanup_4, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Calculate available fruit biomass within HR intervals
Full details here: http://people.ucalgary.ca/~facampos/data/fruit/
```{r calculate_fruit}
```

```{r cleanup_5, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Calculate weather data within HR intervals
Full details here: http://people.ucalgary.ca/~facampos/data/weather/
```{r calculate_weather}
```

```{r cleanup_6, echo=FALSE, message = FALSE, results = 'hide'}
```

<br>
## Load habitat maps and view
```{r load_habitat_maps, message = FALSE, results = 'hide'}
```

<br>
## Calculate home ranges
```{r calculate_hr, eval = FALSE}
```

<br>
## Write utilization distribution raster images to disk
```{r write_ud, eval = FALSE}
```

<br>
## Write hr data to disk
```{r write_hr_data, eval = FALSE}
```

#### Forward to [models](HRModels.html)