Models of home range size and composition
========================================================

#### Up to [data sets](../index.html)
#### Back to [home range calculation](HomeRanges.html)
----
Source files available on [Github](https://github.com/camposfa/HomeRanges)

[Contact me](mailto:camposfa@gmail.com) if you are interested in the raw data


```{r echo=FALSE}
opts_chunk$set(fig.path = 'figure/models/', 
               fig.height = 6, 
               fig.width = 12, 
               tidy = FALSE, 
               warning = FALSE,
               cache = TRUE)
read_chunk('Models.R')
```

<br>
## Prepare workspace
```{r prepare_model_workspace, message = FALSE, results = 'hide'}
```

<br>
## Load home range data
```{r load_hr_data}
```

<br>
## Run models for home range area
```{r area_models}
```

<br>
## Clean up model results for plotting
```{r rename_area_vars}
```

<br>
## Plot results for home range area
```{r plot_area_results}
```

<br>
## Run models for home range composition
```{r ndvi_models}
```

<br>
## Clean up model results for plotting
```{r rename_ndvi_vars}
```

<br>
## Plot results for home range composition
```{r plot_ndvi_results}
```

<br>
## Run models comparing home range zones
```{r zones_model}
```

<br>
## Clean up model results for plotting
```{r rename_zones_vars}
```

<br>
## Plot results comparing home range zones
```{r plot_zones_results, fig.width = 6}
```

```{r model_cleanup, echo=FALSE, message = FALSE, results = 'hide'}
```
